Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
locations

Traditionally, data from each voxel, or from a group of voxels, are analysed with analysis of variance. Voxels are usually convoluted with a haemodynamic response function in an attempt to infer the spiking neural activity from the slowly building and dropping BOLD response \cite{he:2002na}. Figure~\ref{fig:bold_response} depicts such a response function. In this setup, experimental conditions are the independent variables and a general linear model is fitted to each voxel, or group of voxels. By using this technique, voxels or brain areas can be identified that differ in their average BOLD response across conditions.\\

\begin{figure}
	\centering
	\includegraphics[width=60mm]{figures/f1_bold_response}
  	\caption{Above is the hypothetical neural response to some stimulus. Below is the BOLD response that is evoked by the short spike of neural activity. The neural activity shown above is attempted to be inferred from the BOLD response that is measured by the fMRI scanner. Figure is adopted from Heeger and Ress \cite{he:2002na}.}
  	\label{fig:bold_response}
\end{figure}

>>>>

Traditionally, data from each voxel, or from a group of voxels, are analysed with analysis of variance. Voxels are usually convoluted with a haemodynamic response function in an attempt to infer the spiking neural activity from the slowly building and dropping BOLD response \cite{he:2002na} (see Figure~\ref{fig:bold_response}). In this setup, experimental conditions are the independent variables and a general linear model is fitted to each voxel, or group of voxels. By using this technique, voxels or brain areas can be identified that differ in their average BOLD response across conditions.\\
\begin{figure}
	\centering
	\includegraphics[width=60mm]{figures/f1_bold_response}
  	\caption{Above is the hypothetical neural response to some stimulus. Below is the BOLD response that is evoked by the short spike of neural activity. The neural activity shown above is attempted to be inferred from the BOLD response that is measured by the fMRI scanner. Figure is adopted from Heeger and Ress \cite{he:2002na}.}
  	\label{fig:bold_response}
\end{figure}
